Exploiting the Social Graph: Increasing Engagement in a Collaborative Interactive Evolution Application

### 2017-03-13 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Graphs updated
@jj please if you can check the changes, uploading tomorrow.

\begin{abstract}
Interactive evolution, where users' preferences guide the search, is
one of the leading techniques employed by Evolutionary Art
researchers. It is normally implemented as a web application to lower
the access threshold since it often depends on volunteers who visit
the system for fitness assignment. However,  several drawbacks limit
user participation: human fatigue and boredom result from evaluating 
a large number of phenotypes. To tackle these issues, in this paper we
propose an IEC system designed using a human-centered approach, with a
framework consisting of a social network of  
volunteers interacting with a population consisting also of a network 
of phenotypes, which also uses a graph model as a practical 
and efficient tool for mapping the relationships between actors and
objects in the system. A case study is presented as proof-of-concept, 
providing both conceptual and implementation details of a graph based model 
as it is  applied in the implementation of an IEC system. Our
experiments show that the data model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and thus increase {\em performance} of the
interactive system.
\end{abstract}

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure*}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated (X axis) vs. the number of phenotypes evaluated using a logarithmic scale (Y axis). } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

>>>>

\begin{abstract}
Interactive evolution, where users' preferences guide the search, is
one of the techniques employed by Evolutionary Art
researchers. It can be implemented as a web application to lower
the access threshold since it often depends on volunteers who visit
the system for fitness assignment. However, several drawbacks limit
user participation: human fatigue and boredom result from evaluating 
a large number of phenotypes. To tackle these issues, in this paper we
propose an IEC system designed using a human-centered approach, with a
framework consisting of a social network of  
volunteers interacting with a population also consisting of a network 
of phenotypes. The use of a graph model is proposed as a practical 
and efficient tool for mapping the relationships between actors and
objects in the system. A case study is presented as proof-of-concept, 
providing both conceptual and implementation details of the graph model 
as it is  applied in the implementation of an IEC system. Our
experiments show that the data model can be successfully used to implement 
a gamification technique developed to increase users' engagement, which
implies that this technique can be successfully used to 
decrease user fatigue and thus increase the {\em performance} of the
interactive system.
\end{abstract}

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/graphKnows.png}
    \caption{User graph showing the KNOWS relationship (B deployment).}
    \label{fig:B-network}
\end{figure*}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated (X axis) vs. the number of phenotypes evaluated using a logarithmic scale (Y axis). } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}
